NURM: a tool to locate numerical differences in pipelines

### 2019-05-27 paper.tex
Updates in tool description

Figure~\ref{fig:overview} shows an overview of our method. For each 
tested condition, the pipeline is containerized using Docker, and its 
interface is described using Boutiques~\cite{glatard2017boutiques}. 
\reprozip is added to the container images for provenance tracking. Our 
tool first clusters the subjects based on the similarity of their 
process trees produced by \reprozip (Fig.~\ref{fig:overview-cluster}). 
This results in a reduced set of representative process trees to 
evaluate. The processes in each representative process tree are labeled 
from potential differences found in their outputs produced in the 
tested conditions (Fig.~\ref{fig:overview-classify}). To do that, a 
difference file is first produced that contains all the files with 
differences across conditions (Fig.~\ref{fig:overview-classify} - (A)). 
Differences are identified simply by comparing file checksums. 
Using difference file and process tree, we first capture temporary and 
overwritten files in condition 1. In addition, we set various 
breakpoints in the pipeline in condition 2 to check the output files 
produced by each process immediately after running. We then label processes in 4 
categories (Fig.~\ref{fig:overview-classify} - (B)) depending whether 
they create differences (represented in red), remove differences 
(blue), neither create nor remove differences (green), or have 
uncertain behavior (yellow). When processes that create differences are 
found, their written files in condition 2 are replaced (as explained 
later) and then re-labelling processes. This procedure 
continues until the end of the pipeline execution when all processes 
are labeled correctly.

@@

We use \reprozip~\cite{Chirigati2016} to record: (1) 
the tree of processes executed by the pipeline and (2) the list of 
files read and written by each process. This information is collected 
by \reprozip through the \texttt{ptrace} Unix system 
call, and stored in a \texttt{SQLite} database. The database stores 
information of all the processes which are created by the 
\texttt{clone()} or \texttt{fork()} system calls. It also records the 
files opened by each process (in read, write or execution mode), 
including result files and temporary files.

>>>>

Figure~\ref{fig:overview} shows an overview of our method \tristan{add reprozip
tags to 1.b too. Add something to match ``(fixed)'' in 1.b -- cond 2}. For
each tested condition, the pipeline is containerized with Docker, and its
interface is described with Boutiques~\cite{glatard2017boutiques}.
\reprozip~\cite{Chirigati2016} is added to the container images for
provenance tracking. Our tool first clusters the subjects based on the
similarity of their process trees produced by \reprozip
(Fig.~\ref{fig:overview-cluster}) \tristan{``Hclustering'' isn't clear, just
mention ``clustering''}. This results in a reduced set of representative
process trees to evaluate. The processes in each representative process
tree are then labeled from the differences found in their outputs in the
two tested conditions (Fig.~\ref{fig:overview-classify}). To do that, a
difference file is first produced that contains all the differences between
conditions obtained by comparing file checksums
(Fig.~\ref{fig:overview-classify} - (A)). Using the difference file and the
process tree in Condition 1, we first identify temporary files and files
written by more than a single process -- these files result in undetermined
process labels \tristan{Add label in the Figure. Here and for any other step}.
We then label processes in 4 categories (Fig.~\ref{fig:overview-classify} -
(B)) depending whether they create differences (represented in red), remove
differences (blue), neither create nor remove differences (green), or are
undetermined (yellow). Process labelling is done in an iterative way,
through breakpoints and incremental updates in Condition 2, until no
undetermined process remains.

@@

We use \reprozip to record: (1) 
the tree of processes executed by the pipeline and (2) the list of 
files read and written by each process. This information is collected 
by \reprozip through the \texttt{ptrace} Unix system 
call, and stored in a \texttt{SQLite} database. The database stores 
information of all the processes which are created by the 
\texttt{clone()} or \texttt{fork()} system calls. It also records the 
files opened by each process (in read, write or execution mode), 
including result files and temporary files.
